### 2018-03-20 Graduate - Introduction to Analysis II/HW4/4HW20180218.tex
add 5.2.2 b, c

\textbf{(b)} Define $G, l(z), \gamma$ as in Example 2.10, using the same method of Example 2.10, we can show
$$
\int_{0}^{\infty}\frac{(\log x)^2}{1+z^2}dz = 0.
$$
$$
\int_{\gamma}\frac{(l(z))^3}{1+z^2}dz = \int_{r}^{R}\frac{(\log x)^3}{1+x^2}dx + \int_{0}^{\pi}\frac{(\log R+i\theta)^3}{1+R^2e^{2i\theta}}iRe^{i\theta}d\theta + \int_{-R}^{-r}\frac{(\log |x|+\pi i)^3}{1+x^2}dx + \int_{\pi}^{0}\frac{(\log r+i\theta)^3}{1+r^2e^{2i\theta}}ire^{i\theta}d\theta
$$
by residue thm,
$$
\int_{\gamma}\frac{(l(z))^3}{1+z^2}dz = 2\pi i Res(f, i) = -\frac{1}{8}\pi^4 i.
$$
And
$$
\int_{r}^{R}\frac{(\log x)^3}{1+x^2}dx + \int_{-R}^{-r}\frac{(\log |x|+\pi i)^3}{1+x^2}dx = 
$$

>>>>

\textbf{(b)} Define $G, l(z), \gamma$ as in Example 2.10, then
$$
\int_{\gamma}\frac{(l(z))^3}{1+z^2}dz = \int_{r}^{R}\frac{(\log x)^3}{1+x^2}dx + \int_{0}^{\pi}\frac{(\log R+i\theta)^3}{1+R^2e^{2i\theta}}iRe^{i\theta}d\theta + \int_{-R}^{-r}\frac{(\log |x|+\pi i)^3}{1+x^2}dx + \int_{\pi}^{0}\frac{(\log r+i\theta)^3}{1+r^2e^{2i\theta}}ire^{i\theta}d\theta
$$
by residue thm,
$$
\int_{\gamma}\frac{(l(z))^3}{1+z^2}dz = 2\pi i Res(f, i) = -\frac{1}{8}\pi^4 i.
$$
And
$$
\begin{aligned}
\int_{r}^{R}\frac{(\log x)^3}{1+x^2}dx &+ \int_{-R}^{-r}\frac{(\log |x|+\pi i)^3}{1+x^2}dx = \int_{r}^{R}\frac{(\log x)^3+(\log x+\pi i)^3}{1+x^2}dx \\
&= 2\int_{r}^{R}\frac{(\log x)^3}{1+x^2} + 3\pi i\int_{r}^{R}\frac{(\log x)^2}{1+x^2}dx -3\pi^2\int_{r}^{R}\frac{\log x}{1+x^2}dx -\pi^3 i\int_{r}^{R}\frac{1}{1+x^2}dx
\end{aligned}
$$
we know from example 2.10, as $r\to 0, R\to \infty$, the third term is 0, and the last term is
$$
-\pi^3 i\int_{0}^{\infty}\frac{1}{1+x^2}dx = -\frac{1}{2}\pi^4i.
$$
Now we consider the second term. Using the same notation $G, l(z), \gamma$,
$$
\int_{\gamma}\frac{(l(z))^2}{1+z^2}dz = \int_{r}^{R}\frac{(\log x)^2}{1+x^2}dx + \int_{0}^{\pi}\frac{(\log R+i\theta)^2}{1+R^2e^{2i\theta}}iRe^{i\theta}d\theta + \int_{-R}^{-r}\frac{(\log |x|+\pi i)^2}{1+x^2}dx + \int_{\pi}^{0}\frac{(\log r+i\theta)^2}{1+r^2e^{2i\theta}}ire^{i\theta}d\theta
$$
by residue theorem,
$$
\int_{\gamma}\frac{(l(z))^2}{1+z^2}dz = 2\pi i Res(f, i) = -\frac{1}{4}\pi^3.
$$
And
$$
\begin{aligned}
\int_{r}^{R}\frac{(\log x)^2}{1+x^2}dx &+ \int_{-R}^{-r}\frac{(\log |x|+\pi i)^2}{1+x^2}dx = \int_{r}^{R}\frac{(\log x)^2+(\log x+\pi i)^2}{1+x^2}dx \\
&= 2\int_{r}^{R}\frac{(\log x)^2}{1+x^2} + 2\pi i\int_{r}^{R}\frac{\log x}{1+x^2}dx -\pi^2\int_{r}^{R}\frac{1}{1+x^2}dx
\end{aligned}
$$
when $r\to 0, R\to \infty$, the second term is 0, and the last term is
$$
-\pi^2\int_{0}^{\infty}\frac{1}{1+x^2}dx = -\frac{1}{2}\pi^3.
$$
Also, if $\rho > 0$ then
$$
\begin{aligned}
\left|\rho\int_{0}^{\pi}\frac{(\log \rho+i\theta)^2}{1+\rho^2e^{2i\theta}}e^{i\theta}d\theta\right| &\le \rho\frac{|\log\rho|^2}{|1-\rho^2|}\int_{0}^{\pi}d\theta +2\rho\frac{|\log\rho|}{|1-\rho^2|}\int_{0}^{\pi}\theta d\theta +\frac{\rho}{|1-\rho^2|}\int_{0}^{\pi}\theta^2 d\theta \\
&= \rho\frac{|\log\rho|^2}{|1-\rho^2|}\pi + \rho\frac{|\log\rho|}{|1-\rho^2|}\pi^2 + \frac{\rho}{|1-\rho^2|}\frac{\pi^3}{3}
\end{aligned}
$$
let $\rho\to 0^+ $ or $\rho\to\infty$, these terms will be 0. It is just the same for the three-order case, thus
$$
\int_{0}^{\infty}\frac{(\log x)^2}{1+x^2}dx = \frac{1}{8}\pi^3,
$$
hence
$$
\int_{0}^{\infty}\frac{(\log x)^3}{1+x^2}dx = 0.
$$

\textbf{(c)}
First,
$$
\int_{0}^{\infty}\frac{\cos ax}{(1+x^2)^2}dx = \frac{1}{2}\int_{-\infty}^{\infty}\frac{e^{iax}}{(1+x^2)^2}dx.
$$
Let $\gamma = \{|z|=R, Im(z) > 0\} \cup [-R, R]$, then by residue theorem,
$$
\int_{\gamma}\frac{e^{iaz}}{(1+z^2)^2}dz = 2\pi iRes(f, i) = \frac{(a+1)e^{-a}\pi}{2}.
$$
And
$$
\begin{aligned}
\left|\int_{\gamma_R}\frac{e^{iaz}}{(1+z^2)^2}dz\right| &= \left|\int_{0}^{\pi}\frac{e^{-aR\sin\theta}(\cos(aR\cos\theta)+i\sin(aR\cos\theta))}{(1+R^2e^{2i\theta})^2}iRe^{i\theta}d\theta\right| \\
&\le \left|\int_{0}^{\pi}\frac{R}{|1-R^2|^2}d\theta\right| \to 0, ~\text{when} ~R\to\infty.
\end{aligned}
$$
Hence
$$
\int_{0}^{\infty}\frac{\cos ax}{(1+x^2)^2}dx = \frac{(a+1)e^{-a}\pi}{4}.
$$

\textbf{(d)}
